---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ccplot

<!-- badges: start -->
<!-- badges: end -->

The goal of ccplot is to provide out-of-the-box data visualization tools to analyze and understand worldwide greenhouse gas emissions.

## Installation

You can install the development version of ccplot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("omunizb/climate-change")
```

## Usage

Currently, `ccplot` has four plotting functions. The following examples use a [Data on CO2 and Greenhouse Gas Emissions by *Our World in Data*](https://github.com/owid/co2-data) dataset by Hannah Ritchie, Max Roser, Edouard Mathieu and Bobbie Macdonald:

```{r}
Greenhouse_Gas_Emissions <- 
  read.csv("https://raw.githubusercontent.com/owid/co2-data/master/owid-co2-data.csv")
```

- `ccplot::plot_emissions()` draws a plot of annual greenhouse gas emissions for the desired countries or regions.

```{r plot_emissions}
library(ccplot)

plot_emissions(Greenhouse_Gas_Emissions, c("USA", "CHN", "GBR", "RUS"), 
               "Emissions of historical global powers")
```

- `ccplot::decade_increase()` draws a plot of decade-to-decade change in total greenhouse gas emissions (carbon dioxide, methane and nitrous oxide) for the the desired countries or regions and decades.

```{r decade_increase}
library(ccplot)

decade_increase(Greenhouse_Gas_Emissions, c("1990-1999", "1980-1989"), 
                c("USA", "GBR"))
```

- `ccplot::lproj()` draws plots with actual and predicted annual emissions since 1990.

```{r lproj}
library(ccplot)

lproj(df = Greenhouse_Gas_Emissions, region = "USA")
```

- `ccplot::emissions_pred()` draws plots with actual past and projected future annual
greenhouse gas emissions from 1990.

```{r emissions_pred}
library(ccplot)

data(futdata)

emissions_pred(Greenhouse_Gas_Emissions, "USA", futdata)
```

As you can see in this example, `ccplot` also includes the dataset `futdata`with projections of US population and GDP until 2030. 

